---
title: "Student Performance"
description: |
  The success of a student relies on many different factors; knowing how to 
  handle and control these factors will increase a students performance.
site: distill::distill_website
---
## A Quick Glance 

A persons character, personality, all morph and set whilst their in school. Their teachers, the environment they're in, the academic feedback they receive; all set the stones for the path they will pursue in life. In most scenarios, higher academic performance leads to higher satisfaction in the career they pursue.  

Using data from Kaggle, 4 different factors were observed. 

* Ethnicity 
* Gender 
* Parental Level of Education 
* Lunch Type 

These factors were then compared with reading, writing, and math scores. 
 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(ggthemes)
```

## Overview Of Reading Scores

As seen below, ethnic Group D has a tighter range, and denser test scores. Female students have scores higher than the male students for this group; students with a parent holding a masters degree has the smallest range, and an average higher than other levels of education -- this same pattern of parental level of education can be spotted in group C as well. Ethnic groups A, E, and B, can be seen having less students with a parent holding a masters degree, and looser clusters. 

```{r}
student<- read.csv("StudentsPerformance.csv")
student|> 
select(parental.level.of.education, math.score, writing.score, reading.score, gender, race.ethnicity)|> 
ggplot(mapping = aes(y = parental.level.of.education, x = reading.score, color = gender))+
  geom_point(alpha = 0.3, size = 5) + 
  facet_wrap(~race.ethnicity)+ 
  theme_calc()+
  labs(title = "Reading Scores", subtitle = "Cluster of higher scores can be observed for all race groups with a parental 
level of education = Associates Degree", x = "Reading Scores", y = "Parental Level of Education", caption = "Kaggle: JAKKI SESHAPANPU 2018")

```
## Overview of Math Scores 

Compared to reading scores, all groups of scores have higher averages. Male students seem to be dominating higher scores in most groups, and score distrubiton seems to be equal in a few groups (such as group E and A).

```{r}
student<- read.csv("StudentsPerformance.csv")
student|> 
select(parental.level.of.education, math.score, writing.score, reading.score, gender, race.ethnicity)|> 
ggplot(mapping = aes(y = parental.level.of.education, x = math.score, color = gender))+
  geom_point(alpha = 0.3, size = 5) + 
  facet_wrap(~race.ethnicity)+ 
  theme_calc()+
  labs(title = "Math Scores", subtitle = "Male students have higher scores.", x = "Math Scores", y = "Parental Level of Education", caption = "Kaggle: JAKKI SESHAPANPU 2018")
```
## Overview of Writing Scores 

Strongly contrasting the gender distribution for math scores, the higher scores for writing are dominated by female students. This pattern can be observed in every ethnic group, without pause. Similar to the other scores, students with a parent holding a masters degree have a higher score average, and smaller range for all groups except A. Group B and C have the lowest average writing score when parental level of education is "high school" 

```{r}
student<- read.csv("StudentsPerformance.csv")
student|> 
select(parental.level.of.education, math.score, writing.score, lunch, reading.score, gender, race.ethnicity)|> 
ggplot(mapping = aes(y = parental.level.of.education, x = writing.score, color = gender))+
  geom_point(alpha = 0.3, size = 5) + 
  facet_wrap(~race.ethnicity) +
  theme_calc()+
  labs(title = "Writing Scores", subtitle = "Group C and D have a mostly tight range, whereas many outliers are noticable in other ethnic groups.", x = "Writing Scores", y = "Parental Level of Education", caption = "Kaggle: JAKKI SESHAPANPU 2018")
```
These plots, comparing parental level of education, alongside the graphics under the "lunch" page, can lead to many different conclusions and inferences. 

## Summary 


