---
title: "Student Performance"
description: |
  The success of a student relies on many different factors; knowing how to 
  handle and control these factors will increase a students performance.
site: distill::distill_website
---
## A Quick Glance 

A persons character, personality, all morph and set whilst their in school. Their teachers, the environment they're in, the academic feedback they receive; all set the stones for the path they will pursue in life. In most scenarios, higher academic performance leads to higher satisfaction in the career they pursue.  

Using data from Kaggle, 4 different factors were observed. 

* Ethnicity 
* Gender 
* Parental Level of Education 
* Lunch Type 

These factors were then compared with reading, writing, and math scores. 

## Overview Of Reading Scores

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(ggthemes)
```

```{r}
student<- read.csv("StudentsPerformance.csv")
student|> 
select(parental.level.of.education, math.score, writing.score, reading.score, gender, race.ethnicity)|> 
ggplot(mapping = aes(y = parental.level.of.education, x = reading.score, color = gender))+
  geom_point(alpha = 0.3, size = 5) + 
  facet_wrap(~race.ethnicity)+ 
  theme_calc()+
  labs(title = "Reading Scores", subtitle = "Cluster of higher scores can be observed for all race groups with a parental 
level of education = Associates Degree", x = "Reading Scores", y = "Parental Level of Education", caption = "Kaggle: JAKKI SESHAPANPU 2018")

```
```{r}
student<- read.csv("StudentsPerformance.csv")
student|> 
select(parental.level.of.education, math.score, writing.score, reading.score, gender, race.ethnicity)|> 
ggplot(mapping = aes(y = parental.level.of.education, x = math.score, color = gender))+
  geom_point(alpha = 0.3, size = 1) + 
  facet_wrap(~race.ethnicity)+ 
  theme_calc()+
  labs(title = "Math Scores", subtitle = "Male students have higher scores.", x = "Math Scores", y = "Parental Level of Education", caption = "Kaggle: JAKKI SESHAPANPU 2018")
```
```{r}
student<- read.csv("StudentsPerformance.csv")
student|> 
select(parental.level.of.education, math.score, writing.score, lunch, reading.score, gender, race.ethnicity)|> 
ggplot(mapping = aes(y = parental.level.of.education, x = writing.score, color = gender))+
  geom_point(alpha = 0.3, size = 5) + 
  facet_wrap(~race.ethnicity) +
  theme_calc()+
  labs(title = "Writing Scores", subtitle = "Group C and D have a mostly tight range, whereas many outliers are noticable in other ethnic groups.", x = "Writing Scores", y = "Parental Level of Education", caption = "Kaggle: JAKKI SESHAPANPU 2018")
```

