---
title: "Student Performance"
description: |
  The success of a student relies on many different factors; knowing how to 
  handle and control these factors will increase a students performance.
site: distill::distill_website
---

A students success and beneficial academic performance depends on various factors. The following data was pulled from Kaggle. Graphs were used to represent the correlation between test scores and parental level of education, lunch type, race, test preparation, and gender. Students that were not taking a free/reduced lunch, had taken the preparation course, and had parents with an education level above high school were observed to have higher scores.  
 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(ggthemes)
library(plotly)
```

```{r}
student <- read.csv("StudentsPerformance.csv")

# Assign plot to "main" variable 
main <- student|> 
# Select wanted columns to analyze
select(lunch, math.score, writing.score, reading.score, gender, race.ethnicity, parental.level.of.education)|> 
# Using ggplot, start mapping. Assign variables
ggplot(mapping = aes(y = lunch, x = math.score, color = gender))+ 
  # A scatter plot was picked to best show the data
   geom_point(alpha = 0.3, size = 3) +
  # View how parental level of education affects scores by using the function face_wrap
  facet_wrap(~parental.level.of.education) + 
  # Preferred theme was added
  theme_calc() + 
  labs(title = "Factors Affecting Math Test Scores", x = "Math Scores", y = "Lunch Type", caption = "Kaggle: JAKKI SESHAPANPU 2018")  
# Ggplotly was added to make plot interactive 
ggplotly()
```

